\input{Ensembles_Arithmetique/Preamble.tex}

\starttext

  \input{Ensembles_Arithmetique/Titlepage.tex}

  \startbodymatter
    \input{Ensembles_Arithmetique/Theorie_Ensembles.tex} 
    
    \chapter{Introduction}
      \section{Welcome}
        This is the first section of the introduction. We are demonstrating various ConTeXt features.
        We can refer to specific words like \words{ConTeXt}, \words{document}, and \words{features}.
        Let's include some mathematics: $E=mc^2$. This uses the \symbols{$E=mc^2$}{Einstein's mass-energy equivalence} XITS Math font.
        Another equation: $a^2 + b^2 = c^2$.
        \subsection{Getting Started}
          Here's a subsection.
          \subsubsection{Installation}
            Details about installation.

      \section{Overview}
        This section provides an overview.
        \subsection{Structure}
          The document structure.

    \chapter{Advanced Topics}
      \section{Font Handling}
        ConTeXt's font handling is very powerful. We're using \words{XITS} for text and math.
        \subsection{Font Features}
          Exploring OpenType features.
          Some more math: $\int_{-\infty}^{\infty} e^{-x^2} dx = \sqrt{\pi}$.
          We can also index symbols like \symbols{$\int$}{integral sign}.

          \startformula
            e = \frac{m c^2}{\sqrt{1 - v^2 \ds c^2}}
          \stopformula

      \section{Indexing}
        This section is about creating indices.
        We can index more words, like \words{LuaTeX} and \words{OpenType}.

    \chapter{Conclusion}
      \section{Summary}
        A brief summary of the document.
      \section{Next Steps}
        What to do next.
  \stopbodymatter

  \startappendices
    
    \chapter{Some C++ code}
      
      \startCPP
      void negacyclic_ntt_pow2_bit_reversed(
          const uint64_t* const input,
          uint64_t* const output,
          const uint64_t* const powers_root_unity,
          const uint64_t modulus,
          const size_t ntt_size,
          const size_t batch_size = 1);
      \stopCPP

    \input{Ensembles_Arithmetique/Jeux_Entiers.tex} 
  \stopappendices

\startnotmode[export] 
  \startbackmatter
 
    \chapter{Index}
    
    \blank[big]

    \placeregister[wordsRegister]
    
    \chapter{Index des symboles}
    \startcolumns[n=4]
      \placelist[symbolsList]
    \stopcolumns
  \stopbackmatter
\stopnotmode

\stoptext
